### 2016-04-09 ch02-qlogms/excitation-design.tex
Place definition of 3dB BW
Externalize data in {alpha,beta}WC

First, we look at the band-limited $1/f$ power spectrum given by
\begin{align*}
\label{eq:excitation:pink}
\phi_u(\omega) &=\begin{cases}\frac{1}{|\omega|} &\text{if $|\omega|\in[\wn \kMin\; \wn \kMax]$,}\\
                        0           &\text{otherwise}.
            \end{cases}
\end{align*}
With this input spectrum, the power inside $\wdB$ is
\begin{align}
  \frac{1}{2\pi}
    \int\limits_{(1-\damping)\wn}^{(1+\damping)\wn}
     \frac{1}{\omega} \dd{\omega}
  = \frac{1}{2\pi}
    \ln{\frac{1+\damping}{1-\damping}},
\end{align}
which is independent of $\wn$. The robustness of the $1/f$ input has been noted previously by e.g. \citet{Rojas2007,Rojas2012,Goodwin2006GBO}.

@@

  \begin{figure}[pht]
    \centering
      \setlength\figurewidth{0.63\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (see \eqref{eq:excitation:optimAlpha}).}
    \label{fig:excitation:worstCaseBeta}
  \end{figure}

@@

  \begin{figure}[pht]
    \centering
      \setlength\figurewidth{0.63\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
             grid multisines and systems with different peak amplitudes.
             The dashed vertical line represents the optimal frequency spacing $\alpha^{\star}$.}
    \label{fig:excitation:worstCaseAlpha}
  \end{figure}

>>>>

First, we look at the band-limited $1/f$ power spectrum given by
\begin{align*}
\label{eq:excitation:pink}
\phi_u(\omega) &=\begin{cases}\frac{1}{|\omega|} &\text{if $|\omega|\in[\wn \kMin\; \wn \kMax]$,}\\
                        0           &\text{otherwise}.
            \end{cases}
\end{align*}
With this input spectrum, the power inside $\wdB \approx \ClosedInterval{(1-\damping)\wn, (1+\damping)\wn}$ is
\begin{align}
  \frac{1}{2\pi}
    \int\limits_{(1-\damping)\wn}^{(1+\damping)\wn}
     \frac{1}{\omega} \dd{\omega}
  = \frac{1}{2\pi}
    \ln{\frac{1+\damping}{1-\damping}},
\end{align}
which is independent of $\wn$. The robustness of the $1/f$ input has been noted previously by e.g. \citet{Rojas2007,Rojas2012,Goodwin2006GBO}.

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.75\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/betaWC.tikz}
    \caption[Variance $\sigma_G^2\left( \wM \right)$ as a function of the grid misalignment $\beta$.]{Evaluation of the variance $\sigma_G^2\left( \wM \right) $ for different prototype systems as function of the misalignment $\beta$.
             The full lines depict the variance for a coarsely spaced signal.
             The dashed lines show the variance for a signal with the optimal $\alpha = \alpha^{\star}$ (see \eqref{eq:excitation:optimAlpha}).}
    \label{fig:excitation:worstCaseBeta}
  \end{figure}

@@

  \begin{figure}
    \centering
      \setlength\figurewidth{0.75\columnwidth}
      \setlength\figureheight{0.68\figurewidth}
    \input{\thisDir/figs/alphaWC.tikz}
    \caption[Worst-case variance $\sigma_G^2\left( \wM \right)$ as a function of the frequency ratio $\alpha$.]{Worst case variance of the peak in the transfer function for logarithmic
             grid multisines and systems with different peak amplitudes.}
    \label{fig:excitation:worstCaseAlpha}
  \end{figure}
